Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-18 WSSSPE2_report/WSSSPE2_review.tex
Abstract: refine.

\begin{abstract}      
\todo{update abstract}
This technical report discusses the submission and peer-review process used by
the Second Workshop on Sustainable Software for Science: Practice and
Experiences (WSSSPE2) and the results of that process. It is intended to record
both the alternative submission and program organization model used by WSSSPE2
as well as the papers associated with the workshop that resulted from that
process.
\end{abstract}

>>>>

\begin{abstract}      
\todo{update abstract}
This technical report records and discusses the alternative submission and peer-review process used by
the Second Workshop on Sustainable Software for Science: Practice and
Experiences (WSSSPE2) and the results of that process. It is intended to record
both the program-organization model adapted by WSSSPE2
as well as the papers accepted by the workshop.
\end{abstract}
